---
title: "mybincon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mybincon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753GBROSAlab6)
```

# Introduction

This package contains an S3 OOP function, `mybincon`, which performs a simulation of the binomial distribution. It take three items as arguments: `iter` - the number of iterations for the simulation, `n` - the number of each sample, and `p` - the probability. The function produces a bar-plot list containing the following: the simulated probabilities, the true proportion probabilities, the Euclidean Squared Distance between the simulated and the true proportions, the midpoits of the unseen bars, and the simulated matrix.

Also in this package is an accompanying S3 method, `summary.MATH4753GLab6`. This returns a vector of the sample standard deviations with a length of the chosen number of iterations, `iter`.

# Example

The following is an example of the function and it's summary using the following parameters: $iter = 10$, $n = 10$, $p = 0.6$.

```{r}
l <- mybincon(iter = 10, n = 10, p = 0.6)
l
```

```{r}
summary(l)
```

































